A hazards approach to the biometric analysis of infant mortality

### 2023-04-03 Slides/slides.Rmd
improve hazard plot

>>>>

## Biometric analysis on the natural time scale

Given that the exogenous mortality follows an Exponential distribution on the log-cube scale, it follows that the cumulative hazards function on the natural time scale is

\begin{equation*}
H(t; \lambda) = \lambda \log^3(t + 1), \; t > 0,
\end{equation*}

and it follows that the hazard function $h$ is given by

\begin{equation*}
h(t; \lambda) = \frac{3 \log^2(t + 1)}{t + 1}, \; t > 0,
\end{equation*}

## Exogenous mortality on the normal time scale

```{r normal, fig.height = 4}
dg <- function(x) 3 * (log(1 + x))^2 / (1 + x) * 365 / (log(366))^3
oldpar <- par(mfrow = c(1, 2))
x <- 0:365
y <- dg(x)
plot(x, y, type = "l", xlab = "Day", ylab = "Hazards",
     axes = FALSE, col = "blue", lwd = 2, main = "Hazard function")
axis(1, at = c(0, 28, 183, 365))
axis(2, las = 1, at = 0)
box()
abline(h = 0, v = 0)
abline(v = 28, lty = 2, col = "darkgreen")
y <- g(x)
plot(x, y, type = "l", xlab = "Day", ylab  = "Cum. hazards", main = "Cumulative hazards",
     col = "blue")
par(oldpar)
```

## Natural vs. log-cube time scales

Västerbotten 1861--1890.

\includegraphics[width=\textwidth]{../paper2_files/figure-latex/natlogcube2-1.pdf}
